---
title: "Customising `coefplot`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Customising `coefplot`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(coefplot)
dt <- mtcars
dt$cyl <- as.factor(dt$cyl)
model <- lm(mpg ~ wt*disp + cyl, data = dt)
```

## Default arguments

```{r}
coefplot(model)
```

## Labels

### `title`, `xlab`, and `ylab`

```{r}
coefplot(
  model,
  title = 'This is my `coefplot`',
  xlab = 'Coefficient Values',
  ylab = 'Variables'
)
```

### `textAngle` and `numberAngle`

```{r}
coefplot(
  model,
  textAngle = 90,
  numberAngle = 45
)
```

## Coefficients

### `newNames`

```{r}
coefplot(
  model,
  newNames = c('cyl' = 'Cylinder', 'disp' = 'Displacement', 'wt' = 'Weight')
)
```

### `predictors`, `strict`, and `coefficient`

```{r}
coefplot(
  model,
  predictors = c('wt')
)

coefplot(
  model,
  predictors = c('wt', 'disp'),
  strict = TRUE
)

coefplot(
  model,
  coefficient = c('wt', 'cyl')
)
```

### `innerCI`/`outerCI` and `lwdInner`/`lwdOuter` and `pointSize`

```{r}
coefplot(
  model,
  innerCI = 1.5,
  lwdInner = 2,
  outerCI = 3,
  lwdOuter = .5,
  pointSize = 3.5
)
```

### `color`, `shape`, and `linetype`

See the `ggplot2` documentation on [differentiation](https://ggplot2.tidyverse.org/reference/aes_linetype_size_shape.html) to learn more.

```{r}
coefplot(
  model,
  color = 'red',
  shape = 23,
  outerType = 2
)
```

### `intercept`

```{r}
coefplot(
  model,
  intercept = FALSE
)
```

## Display

### `interactive`

```{r}
coefplot(
  model,
  interactive = TRUE
)
```


### `trans`

```{r}
coefplot(
  model,
  trans = \(x) { x * .1 }
)
```


### `zeroColor`, `zeroLWD`, and `zeroType`

```{r}
coefplot(
  model,
  zeroColor = 'red',
  zeroLWD = 2,
  zeroType = 'dotdash'
)
```

### `facet` and `scales`

```{r}
coefplot(
  model,
  facet = TRUE,
  scales = 'free'
)
```

### `sort` and `decreasing`

```{r}
coefplot(
  model,
  sort = 'alphabetical'
)

coefplot(
  model,
  decreasing = TRUE
)
```


