---
title: "Using `coefplot`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using `coefplot`}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(coefplot)
```

## `coefplot()`

`coefplot` provides S3 Methods for `lm`, `glm`, `workflows`, `model_fit`, `rxGlm`, `rxLinMod`, and `rxLogit` objects. These methods take the same arguments as the default `coefplot()` method.

## `coefplot.lm()`

```{r}
lm_model <- lm(mpg ~ wt + cyl*disp, data = mtcars)
coefplot(lm_model)
```

## `coefplot.glm()`

```{r warning=FALSE}
glm_model <- 
  glm(
    mpg > 15 ~ wt + cyl*disp, 
    data = mtcars, 
    family = binomial(link = "logit")
  )
coefplot(glm_model)
coefplot(glm_model, trans = invlogit)
```

## `coefplot.workflow()`

`coefplot.workflow()` plots the coefficients of a fitted `workflows::workflow()` object. Bceause this example is started with a `workflows::workflow()` call, it has the `workflow` class and thus uses `coefplot.workflow()`.

```{r}
workflows::workflow() |>
  workflows::add_formula(mpg ~ wt + cyl*disp) |>
  workflows::add_model(parsnip::linear_reg()) |>
  parsnip::fit(mtcars) |>
  coefplot()
```

## `coefplot.model_fit()`

While `coefplot.model_fit()` passes directly from `parsnip::fit()` to `coefplot()` like in the example for `coefplot.workflow()`, because this example is contained entirely within `parsnip` calls, it has the class `model_fit`.

```{r}
parsnip::linear_reg() |>
  parsnip::set_engine('lm') |>
  parsnip::fit(mpg ~ wt + cyl*disp, data = mtcars) |>
  coefplot()
```
